MSD panels 1, 2 and 3 Explant Supernatant

### 2016-10-07 MSD_panels_1_2_3_explant_sup_analysis.Rmd
Trying to add in minimal values for the places where we have below LOD values from Lamars data so it will show up on the heat map. In complete and untested!!

#I will remove the rows with these samples, AND ALSO the following samples, because they depend on these missing ones for either mock subtraction or T1 mocksubtracted vs T3 mocksubtracted comparison:

#all other samples (i.e. T3) for 304 IL-1a
#all other samples for 304 IL-10

no_missing_only_304_306 <- only_304_306 %>%
  na.omit() %>% #remove the missing samples
  filter(!(Donor == "304" & Assay == "IL-1a"))%>%
  filter(!(Donor == "304" & Assay == "IL-10"))

@@

#one set has 2 members because I am missing 304-T1-V1 for MIP1b. This won't affect the mock subtraction or T1 T3 comparison so I can leave it as is.

@@

```{r LMF data extract and merge mock, echo=FALSE}
#I want to subtract out the mock data from the corresponding v1 and V2 data.

>>>>

#FH asked me to set the concentrations for these "below LOD" data to just below the minimum value for those analytes. I'll subtract 10% of the minimum value and set the below LOD to that.

#get the minimum for the different analytes
MIP1b<-only_304_306 %>%
  filter(Assay == "MIP1b")

lessThanMinMIP1b<-min((na.omit(MIP1b$CalcConc)))-
  0.1 * (min((na.omit(MIP1b$CalcConc))))

IL1a<-only_304_306 %>%
  filter(Assay == "IL1a")

lessThanMinIL1a<-min((na.omit(IL1a$CalcConc)))-
  0.1 * (min((na.omit(IL1a$CalcConc))))

IL10<-only_304_306 %>%
  filter(Assay == "IL-10")

lessThanMinMIP1b<-min((na.omit(IL10$CalcConc)))-
  0.1 * (min((na.omit(IL10$CalcConc))))

#just the samples with nas

missing<- only_304_306[rowSums(is.na(only_304_306)) > 0,]

no_missing <- na.omit(only_304_306)

#fix the missing data
#TEST THIS ####

missing<- missing %>% 
  mutate(CalcConc = 
    ifelse(Assay == "MIP1b" &
            SampleName =="3HR.186.HI",
            lessThanMinMIP1b,
         ifelse(Assay == "IL-1a" &
                  Timepoint == "T1",
                  lessThanMinIL1a, 
           ifelse(Assay == "IL-10" &
                  SampleName == "24HR.Mock.Hi",
                  lessThanMinIL10,CalcConc))))

#Now combine the missing and no missing data and continue....

@@

#all sets are complete since I added in values for the missing data above.

@@

```{r LMF data extract and merge mock, echo=FALSE}
#I want to subtract out the mock data from the corresponding V1 and V2 data.
